%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerlastnamestyle{Minhazur } \headerlastnamestyle{Rahman} \\
	\vspace{2mm}
	{\faEnvelope\ 1605093@ugrad.cse.buet.ac.bd} \hspace{5mm} {\faMobile\ +8801521487070}  \hspace{5mm} {\faMapMarker\ Chattogram , Bangladesh} \hspace{5mm} {\faLink\href{https://minhazrahman.me}{\underline{minhazrahman.me}}}  {\faGithub \href{https://github.com/minhaz725}{\underline{minhaz725}}} \hspace{5mm} {\faLinkedin \href{https://www.linkedin.com/in/minhaz725/}{\underline{Minhazur Rahman}}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BSC in Computer Science and Engineering \newline Final semester (Level -4 , Term -2) ,Running }
	{Bangladesh University of Engineering and Technology (\href{https://www.buet.ac.bd/}{\underline{BUET}})}
	{Dhaka, Bangladesh}
	{February, 2017 – Present}
	{}
\end{cventries}

\vspace{-4mm}

\cvsection{Skills}
\begin{cventries}
	\cventry
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
				Java (Proficient) \hspace{1.2cm} Windows \hspace{1.6cm}  Java Spring Boot (Proficient) \hspace{1cm} HTML \hspace{1.2cm} PostgreSQL \hspace{1.4cm} Git  & {\skill{ }} \\
				C (Proficient) \hspace{1.6cm} Linux \hspace{2.4cm} Ruby on Rails (Familiar)  \hspace{1.3cm} Latex \hspace{1.4cm} MongoDB \hspace{1.4cm} Docker & {\skill{ }} \\
				C++ (Proficient) \hspace{4.7cm} Angular (Proficient) \hspace{1.4cm}   & {\skill{ }} \\
				Python (Familiar) \hspace{4.7cm} React JS (Familiar)  & {\skill{ }} \\
				JavaScript (Proficient) & {\skill{ }} \\ Typescript (Proficient)  & {\skill{ }} \\
				Ruby (Prior Experience)  & {\skill{ }} \\
	\end{tabular}}}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages \hspace{1cm} Operating Systems \hspace{1.2cm} Frameworks \hspace{1.5cm} Markup \hspace{1cm} DataBase \hspace{1cm} Others  & {\skill{ }} \\
		\end{tabular}}}
	{}
	{}
	{}
	
\end{cventries}

\vspace{-7mm}


\cvsection{Experience}
\begin{cventries}
	\cventry
	{Virtual Internship by \href{http://vinternship.org/}{\underline{ESRD Lab}} , BUET.  \href{https://drive.google.com/drive/u/0/folders/1sx3UMH5gBBTkda5ivJqcNqGb4bhuACwu}{\underline{View Certificate}}}
	{Internship}
	{}
	{February, 2021 - March 2021}
	{}
\end{cventries}

\vspace{-7mm}





\cvsection{Projects}

Click on the project titles to visit their github links.
\begin{cventries}
	\cventry
	{Hospital Management System is a web application that uses rest api to store datas of doctors, patients, medicines etc and can do CRUD operations. It can also create a medical report of a patient, which can be downloaded as a pdf.}
	{\href{https://github.com/minhaz725/Hospital-Management-System}{\underline{Hospital Management System}}}
	{Java Spring Boot , Angular , MongoDB}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Known password attack is typically a guessing attack which uses a precompiled list of options. Rather than trying every option, only try complete options which are likely to work. Dictionary attack is kinda similar but it uses a precompiled dictionary wordlist.}
	{\href{https://github.com/minhaz725/Dictionary-And-Known-Password-Attack-On-A-Local-Server}{\underline{Dictionary \& Known Password Attack}}}
	{C, Javascript, Curl}
	{}
	{}
	
	
	\vspace{-5mm}
	\cventry
	{Advanced Encryption Standard is a popular and widely adopted symmetric key encryption algorithm.It is commonly used in a lot of ways, including wireless security, processor security, file encryption, and SSL/TLS. In this project, I created this algo following the following standard rules of AES.}
	{\href{https://github.com/minhaz725/Cryptography-AES}{\underline{Cryptography AES}}}
	{Python}
	{}
	{}
	
	
	\vspace{-5mm}
	\cventry
	{This was the first assignment of our Graphics Lab, where we were asked to draw some objects using the OpenGL library with various operations available.There were three tasks in this assignment.
		1. A Fully Controllable Camera
		2. A Gun
		3. Collision handling of Some Bubbles. }
	{\href{https://github.com/minhaz725/OpenGL-Computer-Graphics}{\underline{OpenGL Computer Graphics}}}
	{OpenGL, C++}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{RoadRash 2D is a simple bike racing game inspired by the classic EA RoadRash.In this game you\textquotesingle{}ll play as a biker with limited bike health and you'll have to compete against other 9 bikers through a busy road with a lot of traffics.}
	{\href{https://github.com/minhaz725/RoadRash2D}{\underline{RoadRash 2D}}}
	{C++ , IGraphics}
	{}
	{}
	
	\vspace{-5mm}
	
	\cventry
	{}
	{To see more of my works and projects, please visit my \href{https://github.com/minhaz725}{\underline{Github}} account. }
	{}
	{}
	{}
	
	\vspace{-5mm}
\end{cventries}

\ 
\end{document}